--- 
title_meta  : Chapter 1
title       : Intro to basics
description : In this chapter, you will take your first steps with R. You will learn how to use the console as a calculator and how to assign variables. You will also get to know the basic data types in R. Let us get started!

--- type:NormalExercise xp:100
## How it works

In the editor on the right you should type R code to solve the exercises. When you hit the 'Submit Answer' button, every line of code is interpreted and executed by R and you get a message whether or not your code was correct. The output of your R code is shown in the console in the lower right corner.

R makes use of the `#` sign to add comments, so that you and others can understand what the R code is about. Just like Twitter! Comments are not run as R code, so they will not influence your result. For example, _Calculate 3 + 4_ in the editor on the right is a comment.

You can also execute R commands straight in the console. This is a good way to experiment with R code, as your submission is not checked for correctness.

*** =instructions
- In the editor on the right there is already some sample code. Can you see which lines are actual R code and which are comments?
- Add a line of code that calculates the sum of 6 and 12, and hit the 'Submit Answer' button.

*** =hint
Just add a line of R code that calculates the sum of 6 and 12, just like the example in the sample code!

*** =pre_exercise_code
```{r eval=FALSE}
# no pec
```

*** =sample_code
```{r eval=FALSE}
# Calculate 3 + 4
3 + 4

# Calculate 6 + 12

```

*** =solution
```{r eval=FALSE}
# Calculate 3 + 4
3 + 4

# Calculate 6 + 12
6 + 12
```

*** =sct
```{r eval=FALSE}
test_output_contains("7", incorrect_msg = "Do not remove the line of R code that calculates the sum of 3 and 4. Instead, just add another line that calculates the sum of 6 and 12.")
test_output_contains("18", incorrect_msg = "Make sure to add a line of R code, that calculates the sum of 6 and 12. Do not start the line with a <code>#</code>, otherwise your R code is not executed!")
success_msg("Awesome! See how the console shows the result of the R code you submitted? Now that you're familiar with the interface, let's get down to R business!")
```

*** =skills
1
